Potential of I/O-Aware Workflows in Climate and Weather

### 2020-05-04 paper.tex
Minor

  \item \textbf{Job} provides the environment with the resources and it runs the user-provided program or script on one of the nodes allocated for it.
  Local variables containing information about the environment of the batch job, e.g., the compute nodes allocated, enacts the Cylc provided script on the node.

>>>>

  \item \textbf{Job} provides the environment with the resources and it runs the user-provided program or script on one of the nodes allocated for it.
  Local variables contain information about the environment of the batch job, e.g., the compute nodes allocated, and they enact the Cylc provided script on the node.
